Rapid technological progress in white light-emitting diodes \\ and its sources in innovation and technology spillovers

### 2023-08-12 2_SSL_NE/article/article_supplementary.tex
added edits

The historical progress in the different sub-efficiencies contributing to overall efficiency (lamp efficiency) is shown in \cref{fgr:subeff}. Context for figure panels is provided below:

@@

>>>>

Empirical data on the historical progress in metrics related to four different sub-efficiencies contributing to the overall LED efficiency (lamp efficiency $\eta_L$) is shown in \cref{fgr:subeff}. Specifically, the figure includes data for forward voltage used to calculate to forward voltage efficiency $\eta_{V_f}$ (Panel A1); efficiency droop $\eta_droop$ (Panel A2); internal quantum efficiency $\eta_IQ$ (Panel B1); and light extraction efficiency $\eta_LE$ (Panel B2). Additional information and context for individual panels in Supplementary \cref{fgr:subeff} are provided below.

@@

Notably, \cref{fgr:subeff} does not include sub-efficiencies related to spectral performance of LEDs: spectral efficiency $\eta_S$ and conversion efficiencies of different phosphors $η_{C_R}$ and $\eta_{C_{Y/G}}$. Typically, there is no direct empirical data available for these metrics in the literature, which made their inclusion in the empirical \cref{fgr:subeff} not relevant. Instead, we calculate the values of these metrics used in Figures 4 and 5 in the main text from spectral and luminous efficacy radiation data presented in \cref{fig:phosphor_spectrum}.
